---
title: "week2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MyPackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
library(dplyr)
library(readr)
library(tidyr)
library(maps)
library(graphics)
library(week2)
```

## Package general information  
This package is intended to be used for getting some information on USA motor crashes.

## Functions  
The user can use the following function:  

### Function ars_summarize_years
This function gets as input a list of years, and gives a summary of how many motor crashes 
there were in each month of each year in USA (taken from relevant files for those years).

##### Function arguments:
**years:** A vector of the years to be read.

##### Function output:
This function returns data frame with a "MONTH" column,
and one columns per each year in the "years" input argument.
The values under each year column - is the number of motor crashes
that happeded in that year - for this specific month.

For example:

```{r fars_summarize_years}
fars_summarize_years(c(2013,2014))
```

### Function fars_map_state
This function gets as input a state number (in USA) and a year.
Its output is a map of this state with points located at the geographical
location of motor crashes that happened in that state in that year.
Note that invalid year (where no file exists for that year), or invalid state number will give an appropriate error.

##### Function arguments:
**state.num:** The state number in USA.  
**years:** A vector of the years to be read.  

##### Function output:
This function returns a map of the specific state with all motor crash locations
That happened in the specific year in that state. All data is taken from relevant file.
For example:

```{r fars_map_state}
fars_map_state(1,2014)
```




